Making Sequential Programs Deterministic

### 2019-03-29 design.tex
todo: replace table with rules
todo: define greek

\todo{Greek letters go after this paragraph.}

@@

\todo{Define the Greek.  For example:

  A type $\tau = \kappa\ \beta$ consists of a qualifier and a basetype.
  Neither may be omitted.

  $\beta$ is a type that lacks its type qualifier, but has type qualifiers
  on any type arguments:
  $\beta = C | C\angles{\overline{\tau}}$.
  }

@@

\begin{table}[]
    \begin{tabular}{|l|l|l|}
        \hline
        \textbf{\<PolyDet>} & \textbf{\PolyDetUp} & \textbf{\PolyDetDown} \\ \hline
        \<NonDet> & \<NonDet> &  \<NonDet>\\ \hline
        \<OrderNonDet> & \<NonDet> &  \<Det>\\ \hline
        \<Det> & \<Det> &  \<Det>\\ \hline
    \end{tabular}
\caption{Polymorphic resolution}
\todo{Write this as a rule rather than a table.}
\label{tab-poly-resolutions}
\end{table}

>>>>

%\todo{Greek letters go after this paragraph.}

@@

%\todo{Define the Greek.  For example:
%
%  A type $\tau = \kappa\ \beta$ consists of a qualifier and a basetype.
%  Neither may be omitted.
%
%  $\beta$ is a type that lacks its type qualifier, but has type qualifiers
%  on any type arguments:
%  $\beta = C | C\angles{\overline{\tau}}$.
%  }

Figure~\ref{typecheck-rules-standard} shows a sample of the standard typing rules applied to 
any typed language. In the generic case, the type $\tau$ represents a valid basetype in a programming language.
\ourTypeSystem extends a basetype with a type qualifier. Throughout this paper, $\tau$ represents a fully qualified type.
In other words, type $\tau = \kappa \ \beta$ consists of both a qualifier $\kappa$ and a basetype $\beta$, neither of which may be omitted.
Further, $\beta$ is a type without a type qualifier, but which has type qualifiers on all its type parameters.
Formally, $\beta ::= C|C \angles{\tau}$ where $C$ represents a Java basetype.

@@

%\begin{table}[]
%    \begin{tabular}{|l|l|l|}
%        \hline
%        \textbf{\<PolyDet>} & \textbf{\PolyDetUp} & \textbf{\PolyDetDown} \\ \hline
%        \<NonDet> & \<NonDet> &  \<NonDet>\\ \hline
%        \<OrderNonDet> & \<NonDet> &  \<Det>\\ \hline
%        \<Det> & \<Det> &  \<Det>\\ \hline
%    \end{tabular}
%\caption{Polymorphic resolution}
%\todo{Write this as a rule rather than a table.}
%\label{tab-poly-resolutions}
%\end{table}

\begin{figure}
    $\infer[\rulename{ordernondet polyup}]
    {\tau \uparrow \ = \|NonDet \ \beta|}
    {\tau \ = \|OrderNonNonDet \ \beta|
        & \wellformed{\tau}
    }$

    $\infer[\rulename{ordernondet polydown}]
    {\tau \downarrow \ = \|Det \ \beta|}
    {\tau \ = \|OrderNonNonDet \ \beta|
        & \wellformed{\tau}
    }$

    $\infer[\rulename{polyup}]
    {\tau \uparrow \ = \kappa \ \beta}
    {\tau \ =\kappa \ \beta
        & \kappa \in \{\|Det, NonDet|\}
        & \wellformed{\tau}
    }$

    $\infer[\rulename{polydown}]
    {\tau \downarrow \ = \kappa \ \beta}
    {\tau \ =\kappa \ \beta
        & \kappa \in \{\|Det, NonDet|\}
        & \wellformed{\tau}
    }$
\caption{Polymorphic resolution}
\label{tab-poly-resolutions}
\end{figure}
